\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-15 papers/jss/article.Rnw
Move the first sentence of the introduction a little back towards the direction of my original version.  Specifically, "manage and control complexity" is redundant, so move back to my "better manage software complexity".  Also add back the "increasingly", as I mentioned in email wanting to make this point specifically -- the utility of this multi-platform pattern becomes more evident with scale and larger code bases, which happens increasingly often now as computer systems get larger.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@790 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Modern data collection and analysis pipelines involve collections
of decoupled components in order to manage and control complexity 
through reusability, modularity, and fault isolation \citep{Wegiel:2010:CTT:1932682.1869479}.
% This is really a different pattern not connected well here.
%Data analysis patterns such as Split-Apply-Combine
%\citep{wickham2011split} explicitly break up large problems into manageable pieces.  
These pipelines are frequently built using different programming 
languages for various phases of data analysis -- collection, 
cleaning, modeling, analysis, post-processing, and
presentation in order to take advantage of the unique combination of
performance, speed of development, and library support offered by
each environment or language. Every stage of such a data
analysis pipeline may produce intermediate results that need to be
stored or sent over the network for further processing. 
% JO Perhaps also mention that serialization is needed for distributed
% systems to make systems scale up?

>>>>

Modern data collection and analysis pipelines increasingly involve collections
of decoupled components in order to better manage software complexity 
through reusability, modularity, and fault isolation \citep{Wegiel:2010:CTT:1932682.1869479}.
% This is really a different pattern not connected well here.
%Data analysis patterns such as Split-Apply-Combine
%\citep{wickham2011split} explicitly break up large problems into manageable pieces.  
These pipelines are frequently built using different programming 
languages for various phases of data analysis -- collection, 
cleaning, modeling, analysis, post-processing, and
presentation in order to take advantage of the unique combination of
performance, speed of development, and library support offered by
each environment or language. Every stage of such a data
analysis pipeline may produce intermediate results that need to be
stored or sent over the network for further processing. 
% JO Perhaps also mention that serialization is needed for distributed
% systems to make systems scale up?
